\documentclass{muratcan_cv}
\usepackage{ragged2e}

\setname{Alex Slepenkov}{}

% \setmobile{+1 333-333-3333}
\setmail{alexmichel249@gmail.com}
\setcitizenship{H-1B Petition valid till Oct 2026}
\setlinkedinaccount{https://www.linkedin.com/in/alex-slepenkov/} 
\setgithubaccount{https://github.com/aslepenkov} 
\setthemecolor{MidnightBlue}

\begin{document}
%Create header
\headerview
\vspace{1ex} % white space
%

\begin{justify}
\text{Senior Full-Stack Engineer with 7+ years of experience developing scalable web applications, cloud-native systems, and microservices. Proven track record delivering high-impact solutions across fintech, GIS, and enterprise platforms. Passionate about problem-solving, team efficiency, and cutting-edge technologies to drive customer success.}
\end{justify}

\section{Education} 
    \datedexperience{Master of Engineering - Computer Science}{Sep 2016 - Jun 2018}
    \explanation{Novosibirsk State University}{Novosibirsk, Russia} 
    \datedexperience{Bachelor of Engineering - Information Systems}{Sep 2012 - Jun 2016}
    \explanation{Karaganda State Technical University}{Karaganda, Kazakhstan}

%
\section{Skills}
    \newcommand{\skillone}{\createskill{Programming Languages}
    {C\# \cpshalf SQL \cpshalf JavaScript \cpshalf TypeScript \cpshalf Python \cpshalf XQuery}}
    %
    \newcommand{\skilltwo}{\createskill{Tools \& Platforms}
  
    {AWS \cpshalf Azure \cpshalf Github CI/CD \cpshalf Jenkins \cpshalf IIS Express \cpshalf Esri (ArcObjects, ArcGIS SDK)}}
    %
    \newcommand{\skillthree}{\createskill{Databases}
    {PostgreSQL  \cpshalf MS SQL Server \cpshalf MongoDB}}
    %
    \newcommand{\skillfour}{\createskill{Technologies}
    {.NET Framework \cpshalf ASP.NET \cpshalf REST APIs \cpshalf Microservices \cpshalf Docker \cpshalf Node.js \cpshalf React.js \cpshalf Angular }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
    \vspace{-3mm} % reduces whitespace!
%



\section{Experience}
    %
    \datedexperience{EPAM Systems}{Dec 2022 - Present}
    \explanation{Software Engineer}{Astana, Kazakhstan}
    \explanationdetail{

     \smallskip
     \coloredbullet\ %
     Delivered a major feature integrating .NET Web API, a .NET Framework monolith, and a console application via Amazon services, decomposition, refinement, and implementation of key user stories.

     \smallskip
     \coloredbullet\ %
     Facilitated daily stand-ups, ensuring smooth team collaboration and progress tracking.
     
     \smallskip
     \coloredbullet\ %
     Optimized database operations, improving query efficiency, and reducing latency.

     \smallskip
     \coloredbullet\ %
     Mentored junior developers, providing guidance on best practices and technical skills.
     
    }
    %
    \datedexperience{2GIS}{Jul 2021 - Dec 2022}
    \explanation{.NET Software Engineer}{Novosibirsk, Russia}
    \explanationdetail{
     \smallskip
     \coloredbullet\ %
     Built a high-throughput SSIS ETL pipeline processing 200M+ rows daily for near real-time analytics.
     
     \smallskip
     \coloredbullet\ %
     Designed and deployed an Excel-to-SQL migration utility, automating manual workflows.
     
     \smallskip
     \coloredbullet\ %
     Implemented CI pipelines and test environments deploy in TeamCity.
    }
    %
    \datedexperience{FG BCS}{Nov 2020 - Jul 2021}
    \explanation{Software Engineer}{Novosibirsk, Russia}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Extended operational data warehouse capabilities to support MetaTrader event ingestion.
     
     \smallskip
     \coloredbullet\ %
     Enhanced error handling and logging mechanisms, reducing incident triage time.

     \smallskip
     \coloredbullet\ %
     Delivered critical backend features for the Data Warehouse support web service, improving  reporting efficiency.
    }
    %
    \datedexperience{XTools Pro, Inc.}{Apr 2018 - Nov 2020}
    \explanation{Junior Software Engineer}{Novosibirsk, Russia}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Developed ArcGIS add-ins with WPF-based UI tools, increasing geodata operations productivity.
     
     \smallskip
     \coloredbullet\ %
     Designed an asynchronous data search algorithm using Task Queues.
     
     \smallskip
     \coloredbullet\ %
     Engineered Excel data integration features, streamlining workflows inside ArcGIS.
    }
    %
    \datedexperience{EPAM Systems}{Jan 2016 - Aug 2016}
    \explanation{Junior Software Engineer}{Karaganda, Kazakhstan}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Built custom VSTO-based UI controls for Microsoft Office suite, improving onboarding experience.
     
     \smallskip
     \coloredbullet\ %
     Set up automated CI/CD pipelines with Jenkins, cutting manual deployment effort.
    }

\section{Pet Projects}
     %
    \datedexperience{dotnetcv}{2025 - Present}
    % \explanation{Creator and Maintainer}{Remote}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
     Building a production-grade template for .NET backend engineers to bootstrap microservices with Docker Compose, PostgreSQL, AWS LocalStack, and React.
     \smallskip
     \coloredbullet\ %
     Emphasizing modern design patterns (Clean Architecture, CQRS, DDD) and best practices for cloud-native development.
    }
    \smallskip
    \datedexperience{intube}{2023 - 2024}
    % \explanation{Creator and Maintainer}{Remote}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Building a social media downloader and file management app using Telegram Bot Api, Docker, Python, and AWS
    }
    \smallskip
    \datedexperience{stonks}{2022 - 2023}
    % \explanation{Creator and Maintainer}{Remote}
    \explanationdetail{
    
    \smallskip 
    \coloredbullet\ %
    Developing a financial portfolio tracking and analysis tool using JavaScript, integrating data from various stock market APIs for real-time price updates and performance monitoring.
    
    \smallskip
    \coloredbullet\ %
    Implementing advanced data processing and visualization techniques to provide users with insights on their portfolio’s performance and future growth predictions.
    
    }

\end{document}
